Paper 3 - Supplementary Information

### 2023-08-02 output/paper/figures.qmd
Using targets to build paper. Checking that labels levels factors are displayed in summary tables.

format:
  pdf:
    pdf-engine: pdflatex
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

@@

<!-- ####################################################################### -->
# CTD Results
<!-- ####################################################################### -->
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10
path <- "../../results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- myphd::load_ctd(path = path, 
                       filter_evidence = TRUE)
myphd::plot_ctd(ctd)
```

>>>>

format:
  pdf:
    pdf-engine: lualatex
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

@@

<!-- ####################################################################### -->
# CTD Results
<!-- ####################################################################### -->
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10
path <- "results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- myphd::load_ctd(path = path, 
                       filter_evidence = TRUE)
myphd::plot_ctd(ctd)
```

### 2023-08-02 output/paper/manuscript.qmd
Using targets to build paper. Checking that labels levels factors are displayed in summary tables.

format:
  pdf:
    pdf-engine: xelatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

@@

<!-- ####################################################################### -->
# Introduction {#intro}
```{r}
#| child: output/paper/sections/introduction.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Methods {#methods}
```{r}
#| child: output/paper/sections/methods.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Results {#res}
```{r}
#| child: output/paper/sections/results.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Discussion {#discussion}
```{r}
#| child: output/paper/sections/discussion.qmd
```
<!-- ####################################################################### -->

>>>>

format:
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}

@@

<!-- ####################################################################### -->
# Introduction {#sec-intro}
```{r}
#| child: output/paper/sections/introduction.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Methods {#sec-methods}
```{r}
#| child: output/paper/sections/methods.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Results {#sec-res}
```{r}
#| child: output/paper/sections/results.qmd
```
<!-- ####################################################################### -->

<!-- ####################################################################### -->
# Discussion {#sec-discussion}
```{r}
#| child: output/paper/sections/discussion.qmd
```
<!-- ####################################################################### -->

### 2023-08-02 output/paper/si.qmd
Using targets to build paper. Checking that labels levels factors are displayed in summary tables.

---
title: "Paper 3 - Tables"

@@

<!-- ####################################################################### -->
# Study populations
<!-- ####################################################################### -->
```{r}

```

<!-- ####################################################################### -->
# Exposures
<!-- ####################################################################### -->
```{r}
#| label: tbl-chem-info
#| tbl-cap: Information about the non-persistent EDCs.
edcs_info <- myphd::edcs_information() |>
  dplyr::select(-c(chem_id, smiles))
gt::gt(edcs_info, groupname_col = "class") |>
  gt::cols_label(
    full_name = "Compound", 
    short_name = "Symbol", 
    pubchem_cid = "PubChem CID", 
    ctd_id = "CTD ID", 
    exposome_explorer_id = "Exposome Explore ID", 
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(columns = everything()), 
    style = list(
      gt::cell_borders(sides = "bottom", weight = gt::px(3)), 
      gt::cell_text(weight = "bold")
    )
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()), 
    style = list(gt::cell_text(weight = "bold"))
  )
```

>>>>

---
title: "Paper 3 - Supplementary Information"

@@
